\documentclass[letterpaper,11pt,oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{ulem}

\usepackage{graphicx}
\usepackage{color}
\usepackage{array}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumitem}
\usepackage{amsmath, mathtools}
\usepackage{datetime}
\usepackage{natbib}
\usepackage{bibentry}

\newdateformat{monthyeardate}{%
  \monthname[\THEMONTH], \THEYEAR}
  \graphicspath{ {images/}} %upload your signature to this file
%Change the margins to fit your CV/resume content
\usepackage[left=0.5in, right=0.5in, bottom=0.5in, top=0.5in]{geometry}

%Skype information - include your Skype name for a link to add you on Skype
\newcommand*{\Skype}{\href{skype:john.smith?add}{john.smith}} 
\newcommand{\Absender}[1][\normalsize]{\Skype} 
\newcommand{\headr}[1]{\uline{\Large{\textbf{#1}} \hfill } \\ \vspace{-0.5cm}}
\renewcommand{\refname}{\headr{Publications}\vspace{-1cm}}
%Changes the page numbers - {arabic}=arabic numerals, {gobble}=no page numbers, {roman}=Roman numerals
\pagenumbering{gobble}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%% NAME OF APPLICANT %%%%%%%%%%%%%%%%%%%
%
\indent\vspace{0.2cm}\LARGE{\textbf{Daniel Ames Messenger} \hfill \textbf{\monthyeardate\today}} \\ %\vspace{-2ex}
%\hline 
\normalsize
%
%%%%%%%%%%%%%%%%% CONTACT INFORMATION %%%%%%%%%%%%%%%%%
% Your email address, website, and Skype name are links to send email, open your website and add you on Skype. 
%
\indent Director's Postdoctoral Fellow
\hfill \href{mailto:daniel.messenger@colorado.edu}{daniel.messenger@colorado.edu} \\
\indent Theoretical Division, Los Alamos National Laboratory (LANL) \hfill  \url{https://dm973.github.io} \\

%%%%%%%%%%%%%%%%% MAIN BODY %%%%%%%%%%%%%%%%%%%%%%%%%%%
% The main body is contained in a tabular environment. To move sections onto the next page, simply end the tabular environment and begin a new tabular environment.
%\vspace{5mm}

\headr{Education}

\vspace{0.5cm}
\begin{tabular}{@{} p{0.01cm} @{} p{4.3cm} @{} p{5.7cm} @{} p{8cm}@{} }
& Aug. 2019 - Aug. 2022 & \textbf{PhD} Applied Mathematics & University of Colorado Boulder (UCB)\\ 
& Aug. 2017 - July 2019 & \textbf{MS} Applied Mathematics & Simon Fraser University (SFU)\\ 
& Sept. 2011 - May 2015  & \textbf{BS} Mathematics, \textbf{BA} Physics & University of Puget Sound (UPS)
\end{tabular}
\vspace{0.5cm}

%\headr{Research Interests}

%\begin{tabular}{@{} p{0.01cm} @{} p{16.5cm}@{} }
% & Model selection and parameter estimation from data, weak-form algorithms, applications to collective dynamics (cell migration, plasma physics, financial markets, autonomous robots, etc).
%\end{tabular}

\headr{Research Experience}

\vspace{0.5cm}
\begin{tabular}{@{} p{0.01cm} @{} p{4cm} @{} p{16cm}@{} }
& 10/2024 - (current)  & 
\textbf{Director's Postdoctoral Fellow.}, T-5 Division; LANL \\
& 08/2023 - 10/2024  & 
\textbf{Research Associate}, Applied Math, UCB; Bortz lab \\
& 08/2022 - 08/2023 & 
\textbf{Postdoctoral Research Associate}, Applied Math, UCB; Bortz lab\\
& 08/2020 - 08/2022  & 
\textbf{Research Assistant}, Applied Math, UCB; 
Advisor: Dr. Bortz \\
& Summers 2018, 2019  & 
\textbf{Research Assistant}, Math, SFU; Advisors: R. Fetecau, R. Wittenberg
%& Summer 2014  & \textbf{Research Intern}, Pacific Northwest National Lab (PNNL) 
\end{tabular}
\vspace{0.5cm}


\bibliographystyle{plain}
\nobibliography{bib_short.bib}

\headr{Publications}

\begin{itemize}
\itemsep0em 
\item \bibentry{minor2025learning}
\item \bibentry{burby2024non}
\item \bibentry{wang2024physics}
\item \bibentry{bonneville2024comprehensive}
\end{itemize}
\begin{enumerate}[label={[\arabic*]}]
\itemsep0em 
\item \bibentry{vasey2023influence}
\item \bibentry{messenger2024weakeco}
\item \bibentry{messenger2024asymptotic}
\item \bibentry{RUSSO202497}
\item \bibentry{messenger2024coarse}
\item \bibentry{BortzMessengerTran2024NumericalAnalysisMeetsMachineLearning}
\item \bibentry{tran2024weak}
\item \bibentry{bortz2023direct}
\item \bibentry{messenger2022learninganisotropic}
\item \bibentry{fetecau2018zero}
\item \bibentry{messenger_online_2022}
\item \bibentry{messenger2021learning}
\item \bibentry{messenger_weak_2021}
\item \bibentry{messenger_weak_2021-1}
\item \bibentry{messenger_equilibria_2020}
\end{enumerate}

\headr{Awards \& Scholarships}

\begin{enumerate}[label={[\arabic*]}]
\itemsep0em 
\item (2024) LANL Director's Postdoctoral Fellowship \hfill 
\item (2024) NSF MSPRF (Declined)\hfill  
\item (2023) HLFF 10th Heidelberg Laureate Forum Young Researcher \hfill 
\item (2022) SIAM Graduate Student Travel Award (MDS22) \hfill 
\item (2019) UCB Special Entrance Scholarship \hfill  
\item (2019) SFU MSc Thesis Certificate with Distinction \hfill 
\end{enumerate}

%\begin{tabular}{@{} p{0.00cm} p{1cm} p{9cm} p{8cm}}
%& 2024 & Director's Postdoctoral Fellowship, T-5 Division & Los Alamos National Labs \\
%& 2024 & (Declined) MSPRF & NSF \\
%& 2023 & 10th Heidelberg Laureate Forum Young Researcher & HLFF \\
%& 2022 & Graduate Student Travel Award (MDS22) & SIAM \\
%& 2019 & Special Entrance Scholarship & UCB \\
%& 2019 & MSc Thesis Certificate with Distinction & SFU \\
%%& 2018 & Best Poster Award & SFU Summer Symposium \\
%%& 2018 & Graduate Fellowship & SFU \\
%%& 2017 & Special Entrance Scholarship & SFU \\
%%& 2015 & Successful Participant & Mathematical Contest in Modeling \\
%%& 2011-2015 & Dean’s Scholarship & UPS\\
%%& 2012-2014 & Hoffman Construction Scholarship & UPS\\ 
%\end{tabular}

\headr{Press}
\begin{sloppypar}
\begin{enumerate}[label={[\arabic*]}]
\itemsep0em 
\item 
\raggedright``The Weak Form is Stronger than you Think'', DAM et al., Oct.\ 1, 2024. {\it SIAM News}. {\footnotesize\url{www.siam.org/publications/siam-news/articles/the-weak-form-is-stronger-than-you-think/}}.
\item 
\raggedright``On Data-Driven Equation Discovery'', George Miloshevich, Dec. 1, 2023. Towards Data Science. {\footnotesize\url{https://towardsdatascience.com/on-data-driven-equation-discovery-5069795d239d}}.
\item 
\raggedright``Researchers strive to help models learn from ‘noisy’ data''. Oct. 23, 2023. University of Colorado Boulder Arts \& Sciences Magazine. {\footnotesize\url{https://www.colorado.edu/asmagazine/2023/10/23/researchers-strive-help-models-learn-noisy-data}}.
\item 
\raggedright``APPM Research Associate Daniel Messenger selected for Heidelberg Laureate Forum'', Patrick McCreery, July 24, 2023. Applied Mathematics News, CU Boulder. {\footnotesize\url{https://www.colorado.edu/amath/2023/07/24/appm-research-associate-daniel-messenger-selected-heidelberg-laureate-forum}}.
\item \raggedright``New study shows how to learn the equations of cell migration'', Daniel Strain. Oct 26, 2022. CU Boulder Today. {\footnotesize\url{https://www.colorado.edu/today/2022/10/26/new-study-shows-how-learn-equations-cell-migration}}.
\item 
\raggedright``CU Boulder joins national effort to advance nuclear fusion research''. Oct 19, 2022. University of Colorado Boulder Arts \& Sciences Magazine. {\footnotesize\url{https://www.colorado.edu/asmagazine/2022/10/19/cu-boulder-joins-national-effort-advance-nuclear-fusion-research}}.
\end{enumerate}
\end{sloppypar}

\headr{Presentations, Posters, Workshops - 2024}

\begin{enumerate}[label={[\arabic*]}]
\itemsep0em 

\item \textbf{Weak-Form Equation Learning: Future Directions}. CHaRMNET Annual Meeting, Virginia Tech, Blacksburg, VI. Dec. 3, 2024.

\item \textbf{Weak-form Inference of Hybrid Dynamics in
Ecology: Coding Tutorial} (Workshop leader). U. Colorado Boulder \& U. Chicago (virtual). Aug.\ 21st, 2024.

\item \textbf{Recent advances in weak-form equation learning
with applications to multiscale phenomena}. WCCM 2024, Vancouver, Canada. July.\ 23rd, 2024.

\item \textbf{Recent Advances in Weak-form Equation Learning}. SIAM Annual 
Meeting 2024, Spokane, WA. July.\ 10th, 2024.

\item \textbf{Adventures of an Applied Mathematician} (Workshop leader). Calculus A/B, Peak-to-Peak High School. Lafayette, CO. May 17, 2024.

\item \textbf{Interacting Particle Systems: Analysis, Control, Learning and Computation} (Workshop participant). ICERM, Providence, RI. May 6-10, 2024.

\item \textbf{Weak-form equation learning with applications to cell migration and general multiscale phenomena}. Applied Mathematics Seminar, University of Waterloo, Ontario, CA. Feb. 1st, 2024.

\end{enumerate}

\headr{Presentations $(<2024)$}

\begin{enumerate}
\item (Contributed) \textbf{Recent advances in Weak-Form Equation Learning with
applications to collective cell migration}. Mathematical Biology Seminar, University of Colorado, Boulder, CO. Oct. 31, 2023.
\item (Invited) \textbf{Weak-form equation learning using WSINDy}. Presentation for T-5 Group, Theoretical Division, Los Alamos National Laboratory, NM. Sept. 1st, 2023.
\item (Invited) \textbf{Weak Form Equation Learning for Interacting Particle System
Models of Collective Motion}. ICIAM 2023, Tokyo. Aug. 23, 2023.
\item (Invited) \textbf{Recovery guarantees and statistical efficiency in weak-form
system identification}. Center for Stochastic Dynamics Summer Seminar, Illinois Institute of Technology, July 26, 2023.
\item (Invited) \textbf{Weak-Form Equation Learning for Interacting Particle System Models of Collective Motion}. SIAM Dynamical Systems 2023, Portland, OR. May 17, 2023.
\item (Invited) \textbf{A Crash Course in Differential Geometry, Hamiltonian Systems, and Adiabatic Invariants in the Context of Data-Driven Modeling}. SIAM Graduate Student Chapter Seminar, University of Colorado, Boulder, CO. April 20, 2023.
\item (Invited) \textbf{Towards recovery guarantees and statistical efficiency in weak-form system identification}. Computational Mathematics Seminar, University of Colorado, Boulder, CO. April 17, 2023.
\item (Contributed) \textbf{Weak-form System Identification: Computational Efficiency and Applications to MHD}. SIAM CSE23, Amsterdam, NL. Mar. 1st, 2023.
\item (Invited) \textbf{Weak-Form Sparse Identification of Models for Cell Biology at Single-Cell and Population Level Descriptions}. Joint Mathematics Meetings, Boston, MA. Jan. 6, 2023.
\item (Invited) \textbf{Weak-form sparse identification of differential equations from noisy measurements}. SFU Applied and Computational Math Seminar, Burnaby, BC. Oct. 7, 2022.
\item (Invited) \textbf{Using WSINDy to Learn Anisotropic Interaction 
Rules from Individual Trajectories in a Heterogeneous Cellular Population}. SIAM Conference on Mathematics of Data Science (MDS22), San Diego, CA. Sept. 28, 2022.
\item (Contributed) \textbf{Online Weak-form Sparse Identification of Partial Differential Equations}. Mathematical and Scientific Machine Learning 2022 (MSML2022), Beijing, China. Aug. 16, 2022.
\item (Invited) \textbf{Data-Driven Model Selection using Weak SINDy}. T-5 Reading Group, Theoretical Division, Los Alamos National Laboratory, NM. Aug. 6, 2021.
\item (Invited) \textbf{Data-Driven Model Selection using Weak SINDy}. APPM Recruitment Symposium, University of Colorado, Boulder, CO. March 5, 2021.
\item (Invited) \textbf{Data-Driven Model Selection using Weak SINDy}. Mathematical Biology Seminar, University of Colorado, Boulder, CO. Sept. 21, 2020.
\item (Contributed) \textbf{Aggregation-Diffusion Phenomena in Domains with Boundaries}. SIAM Front Range Student Conference, University of Colorado, Denver, CO. March 7, 2020.
\item (Invited) \textbf{Aggregation-Diffusion Phenomena in Domains with Boundaries}. Mathematical Biology Seminar, University of Colorado, Boulder, CO. Dec. 10, 2019.
\item (Contributed) \textbf{Aggregation-Diffusion Phenomena in Domains with Boundaries}. Canadian Applied and Industrial Mathematics Society (CAIMS), Annual Meeting, Whistler, BC. June 10, 2019.
\item (Invited) \textbf{Self-Organization in Domains with Boundaries}. Math Graduate Seminar, Simon Fraser University, Burnaby, BC. July 12, 2018.
\item (Invited) \textbf{Normal and Enhanced Vibrational Spectroscopy}. Fall Physics Research Symposium, University of Puget Sound, Tacoma, WA. Oct. 17, 2014.
\item (Invited) \textbf{Normal and Enhanced Vibrational Spectroscopy}. Summer Intern Research Symposium, Pacific Northwest National Laboratory, Richland, WA. July 28, 2014.
\end{enumerate}

\headr{Posters $(<2024)$}
\vspace{-0.5cm}
\begin{enumerate}[label={[\arabic*]}]
\item \textbf{Coarse-Graining Hamiltonian Systems Using WSINDy}. APPM Graduate Student Recruitment Poster Session, CU Boulder. March. 13, 2024.
\item (Invited) \textbf{Coarse-Graining Hamiltonian Systems Using WSINDy}. ChaRMNET Annual Meeting, MSU, East Lansing, MI. Dec. 4, 2023.
\item (Invited) \textbf{Data-Driven Model Selection using Weak SINDy}. Inaugural Workshop: AI for Dynamic Systems, University of Washington, Seattle, WA. March. 16, 2022.
\item (Invited) \textbf{Data-Driven Model Selection using Weak SINDy}. APPM Recruitment Symposium, University of Colorado, Boulder, CO. March. 11, 2022.
\item (Contributed) \textbf{Weak SINDy: Galerkin-Based Data-Driven Model Selection}. SAMM 2020, Max Planck Institute for Dynamics of Complex Systems, Magdeburg, GE. July 27, 2020.
\item (Contributed) \textbf{Interacting Particle Systems: Numerics for the Zero-Diffusion Limit}. Canadian Mathematical Society (CAS), Winter Meeting, Vancouver, BC. Dec. 7, 2018.
\item (Contributed) \textbf{Random Interacting Particle Systems: Numerics for the Zero-Diffusion Limit}. SFU Symposium on Mathematics and Computation, Burnaby, BC. Aug. 14, 2018.
\item (Contributed) \textbf{Normal and Enhanced Vibrational Spectroscopy}. Fall Research Poster Session, University of Puget Sound, Tacoma, WA. Sept. 11, 2014.
\end{enumerate}

\headr{Workshops $(<2024)$}
\vspace{-0.5cm}
\begin{enumerate}[label={[\arabic*]}]
\item \textbf{CHaRMNET Annual Meeting}. MSU, East Lansing, MI. Dec. 4-6, 2023.
\item \textbf{Weak-form system identification and parameter estimation}. Workshop organized by N. Mangan, virtual, Aug. 8, 2023.
\item \textbf{Weak Derivatives and the real world} (Workshop leader). Calculus A/B, Peak-to-Peak High School. Lafayette, CO. May 15, 2023.
\item \textbf{WENDy tutorial in MATLAB}. Guest lecture and workshop, APPM 4720 Data-Driven Modeling, UCB. Mar. 23 \& April 4, 2023.
\item \textbf{WSINDy\_PDE tutorial in MATLAB}. Guest lecture and workshop, APPM 4720 Data-Driven Modeling, UCB. Feb. 16, 2023.
\item \textbf{Mathematical modeling with differential equations} (Workshop leader). 
Calculus A/B, Peak-to-Peak High School. Lafayette, CO. Dec 9, 2022.
\item \textbf{WSINDy MATLAB tutorial: ODEs \& PDEs}. Guest lecture and workshop, APPM 4720 Data-Driven Modeling, UCB. April 5 \& 7, 2022.
\item \textbf{Learning Models from Data: Model Reduction, System Identification and Machine Learning}, GAMM Juniors' Summer School on Applied Mathematics and Mechanics (SAMM 2020), Max Planck Institute for Dynamics of Complex Systems, Magdeburg, GE. July 27, 2020.
\end{enumerate}

\headr{Teaching}
%\begin{tabular}{@{} p{0.01cm} @{} p{5.5cm} @{} p{12.5cm}@{} }
\begin{tabular}{p{0.01cm} p{4.5cm} p{12cm}}
%\begin{tabular}{@{} p{0.01cm} p{2cm} p{14cm}}
& 2020--2021 & \textbf{Co-Instructor}, Department of Applied Mathematics, UCB \\
&     & APPM 7400 Teaching Excellence (Fall 2020)\\ \vspace{-0.75cm}
%&&\\\vspace{-0.75cm}
& 2019-- 2020 & \textbf{Teaching Assistant}, Department of Applied Mathematics, UCB \\
&     & APPM 1350 Calculus I (Fall 2020)\\
&     & APPM 2360 Differential Equations (Spring 2020)\\
&     & APPM 2350 Calculus III (Fall 2019)\\
%&&\\
& 2017--2019  & \textbf{Teaching Assistant}, Department of Mathematics, SFU  \\
&     & MACM 316 Numerical Analysis (Spring 2019) \\
&     & MATH 303 Set Theory and Logic (Fall 2018) \\ 
&     & Math 310 Differential Equations (Spring 2018) \\ 
&     & Calculus I,II,III (Fall 2017)\\
%&&\\
& 2015  &\textbf{Lab Assistant}, Physics Department, UPS \\
&     & PHYS 110 College Physics 2 (Spring 2015) \\
\end{tabular}


\headr{Professional Service}
\begin{tabular}{p{0.01cm} p{4.5cm} p{12cm}}
& (ongoing) & {\bf Reviewer} (10+ journals)\\
& May 10$^\text{th}$, 2023 & {\bf Calculus workshop leader}, Peak to Peak High School, Colorado \\ 
& Dec. 9$^\text{th}$, 2022 & {\bf Calculus workshop leader}, Peak to Peak High School, Colorado \\ 
& Fall 2021 - Spring 2022 & \textbf{President}, SIAM graduate student chapter, UCB\\
& Fall 2021 - Spring 2022  & \textbf{Peer mentor}, Department of Applied Mathematics, UCB\\
& Fall 2021  & \textbf{Organizer, Co-creator}, APPM Graduate Student Seminar, Department of Applied Mathematics, UCB\\
& Summer 2020 - Spring 2021 & \textbf{Lead Teaching Assistant}, Center for Teaching and Learning \& Department of Applied Mathematics, UCB\\
& Spring 2020, Spring 2021, Spring 2022  & \textbf{Organizer}, SIAM Front Range Student Conference \\
& Fall 2019  & \textbf{Secretary}, SIAM graduate student chapter, UCB\\
& Fall 2018 - Summer 2019 & \textbf{Vice President}, grill master, ski-trip organizer, Math Graduate Caucus, SFU\\
& Spring 2019 & \textbf{Councilor}, Graduate Student Society, SFU\\
& Fall 2019 - Spring 2019 & \textbf{Committee Member}, Internal Relations Committee, Teacher and Support Staff Union, SFU \\
\end{tabular}


%\headr{Programming Languages}

%MATLAB, \LaTeX, Git, Bash, Python, Mathematica\\

%\headr{General Work Experience}

%\begin{tabular}{@{} p{0.01cm} p{4.5cm} p{5cm} p{12cm}}
%& Fall 2016-Summer 2017 & \textbf{Math and Physics Tutor} & Fusion Math, Seattle, WA\\
%& Fall 2016-Summer 2017 & \textbf{IT Technician} & Jet City IT, Seattle, WA\\
%& Summer 2016 & \textbf{Logistics Manager, \newline Kayak guide} & Mountain Travel Sobek, Gustavus, AK\\
%& Summer 2015 - Spring 2016 & \textbf{Sales Representative} & Reliable Credit Assoc., Federal Way, WA\\
%\end{tabular}

%\Large{Professional} & American Mathematical Society (AMS)\\
%\Large{Memberships} & Canadian Mathematical Society (CMS)\\
%& Society for Industrial and Applied Mathematics (SIAM)\\

\end{document}

